---
title: "SRT411 Assignment 0"
author: "Joshua Reddy"
date: "January 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##ToDo 1
Compute the difference between 2014 and the
year  you  started  at  this  university  and  divide
this by the difference between 2014 and the year
you  were  born.   Multiply  this  with  100  to  get
the  percentage  of  your  life  you  have  spent  at
this university.  Use brackets if you need them.

```{r todo1}
((2017-2015)/(2017-1997))*100
```


##Todo 2
Repeat  the  previous  ToDo,  but  with  several
steps  in  between.   You  can  give  the  variables
any name you want, but the name has to start
with a letter.

```{r todo2}
t <- 2017-2015 #represents time spent at Seneca
l <- 2017-1997 #represents time spent alive
t/l*100
```

##Todo 3
Compute the sum of 4, 5, 8 and 11 by first com-bining them  into  a  vector  and  then  using  the function sum.

```{r todo3, eval=FALSE}
sum(c(4,5,8,11))
```
The sum of 4, 5, 8 and 11 is `r sum(c(4,5,8,11))`

##Todo 4
Plot 100 normal random numbers.

```{r todo4}
x <- rnorm(100)
plot(x)
```

##Todo 5
Find help for the sqrt function

```{r todo5}
help(sqrt)
#or
?sqrt()
```

##Todo 6
Make a  le calledfirstscript.R containing R- code that generates  100  random  numbers  and plots them, and run this script several times.

[firstscript.R](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/firstscript.R)
```{r todo6a, eval=FALSE}
#contents of firstscript.R
x <- rnorm(100)
plot(x)
```

```{r todo6b}
source("firstscript.R")
source("firstscript.R")
source("firstscript.R")
```

##Todo 7
Put the numbers 31 - 60 in a vector named P and in a matric with 6 rows and 5 columns named Q. Tip: use the function seq. Look at the different types of ways scalars, vectors and matrices are denoted in the workspace window.

```{r todo6}
P <- seq(from=31, to=60)
Q <- matrix(P, nrow=6, ncol=5)
Q
```

##Todo 8
Make a script file which constructs three ran-
dom normal vectors of length 100. Call these
vectors x1, x2 and x3. Make a data frame called
t with three columns (called a, b and c) con-
taining respectively x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame:
plot(t) and sd(t). Can you understand the
results? Rerun this script a few times.

[secondscript.R](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/secondscript.R)
```{r todo8a, eval=FALSE}
#contents of secondscript.R
x1<-rnorm(100)
x2<-rnorm(100)
x3<-rnorm(100)

t<- data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
```

```{r todo8b}
source("secondscript.R")
plot(t)
sapply(t, sd) #sd does not work with data.frames anymore
```
```{r todo8c, echo=FALSE}
source("secondscript.R")
plot(t)
sapply(t, sd)

source("secondscript.R")
plot(t)
sapply(t, sd)
```

The results are ...


#ToDo 9
Add these lines to the script file of the previous
section. Try to find out, either by experiment-
ing or by using the help, what the meaning is of
rgb, the last argument of rgb, lwd, pch, cex.

[thirdscript](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/thirdscript.R)
```{r todo9a, eval=FALSE}
#contents of thirdscript.R
x1<-rnorm(100)
x2<-rnorm(100)
x3<-rnorm(100)

t<- data.frame(a=x1, b=x1+x2, c=x1+x2+x3)

#added lines
plot(t$a, type="l", ylim=range(t),
     lwd=3, col=rgb(0.9,0,0,0.9))
lines(t$b, type="s", lwd=2,
      col=rgb(0,0.9,0,0.9))
points(t$c, pch=4, cex=1,
       col=rgb(0,0,1,0.9))
```

```{r todo9b, echo=FALSE} 
source("thirdscript.R")
```

###Meanings of Graphical Parameters
rgb = Red, Green, Blue and Alpha Colour Specification where alpha is the opacity of the color.

lwd = Line width relevant to default = 1.

pch = Specify symbol for plot points.

cex = The number that the plot text and symbols should be scaled to. 1 = default, 0.5 = 50% of default, 1.5 = 150% of default.

##Todo 10
Make a file called tst1.txt in Notepad from
the example in Figure 4 and store it in your
working directory. Write a script to read it, to
multiply the column called g by 5 and to store
it as tst2.txt.

[tst1.txt](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/tst1.txt)
```{r todo10a}
x<- read.table(file="tst1.txt", header = TRUE)
x

```

[fourthscript.R](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/fourthscript.Rs)
```{r todo10b, eval=FALSE}
#Contents of fourthscript.R
a<-data.frame(read.table(file="tst1.txt", header = TRUE));
a$g = a$g*5
write.table(a, file="tst2.txt", row.names = FALSE)

```

[tst2.txt](https://github.com/joshreddy/SRT411-Assignment-0/blob/master/tst2.txt)
```{r todo10c}
z<- read.table(file="tst2.txt", header = TRUE)
z
```


##Todo 11
Compute the mean of the square root of a vec-
tor of 100 random numbers. What happens?

```{r todo11, warning=FALSE}
w <- rnorm(100)
mean(sqrt(w))
```

The result is NaN, which means 'not a number'. 

You cannot square root negative numbers. It will give a NaN value.

```{r todo11a, warning=FALSE}
sqrt(w)
```

When the mean() function runs it cannot get the mean of non-numbers. This will return an error with the result of NaN.


##Todo 12
Make a graph with on the x-axis: today, Sin-
terklaas 2014 and your next birthday and on
the y-axis the number of presents you expect on
each of these days. Tip: make two vectors first.

```{r todo12}
x<-strptime( c("20170124", "20171118", "20170621"), format="%Y%m%d")
#0 Presents today, 1 Present on Sinterklaas 2017, 20 Presents on my birthday.
y<- c(0,1,20)

plot(x,y, type="p", pch=8, cex=1.5, xlab="Date", ylab="Number of Presents", col=rgb(1,0,0,1) )

```

#Todo 13
Make a vector from 1 to 100. Make a for-loop
which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.

```{r todo13}
e <- seq(from=1, to=100, by=1)
k <- c()
for(i in 1:100)
{
  if (e[i]<5)
  {
    k[i]=e[i]*10;
  }
  else if (e[i]>90)
  {
    k[i]=e[i]*10;
  }
  else
  {
    k[i]=e[i]*0.1;
  }
}
k

```

##Todo 14
Write a function for the previous ToDo, so that you can feed it any vector you like (as argument). Use a for-loop in the function to do the computation with each element. Use the standard R function length in the specification of the counter.

```{r todo14, eval=FALSE}
fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
}



```
